---
title: "CLT"
author: "Sisilia Martinez"
date: '2022-06-08'
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")
my1000 <- sample(Homers_data$kkardashtemp ,size = 1000, replace=T)
densityplot(my1000,main="original data")
Originalmean<-mean(my1000)
originalSD<-sd(my1000)
options(digits=1)
```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

The mean on the original data is `r Originalmean` standard deviation is `r originalSD`

Now take 2 random samples of 1000 points of the kkardashtemp variable and form 1000 points of their averages,

```{r}
numb = 2
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
sample2mean<-mean(x.avg)
sample2sd<-sd(x.avg)
``` 

The plot is not unimodal. In this plot it contains three peaks for a sample size of two. The left peak and the right peaks are both the same size however the peak in the middle is greater than the left and right peak. The average is `r sample2mean` nd the standard deviation is `r sample2sd`

```{r}
numb = 4
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 4")
sample4mean<-mean(x.avg)
sample4sd<-sd(x.avg)
```

 The mean for this sample is `r sample4mean` and the standard deviation is `r sample4sd`. There are five peaks in the sample. 1 out of 4 people disliking her, 2 out of 4 people liking her , and lastly 4 out 4 people liking her. With the highest peak being 2 out of 4 people liking her.

```{r}
numb = 9
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 9")
sample9mean<-mean(x.avg)
sample9sd<-sd(x.avg)
```

 The mean for this sample is `r sample9mean` and the standard deviation is `r sample9sd`. Looking at the graph you can see that there is 4 small bumps. The small bumps are visuals of how the data shifts.

```{r}
numb = 16
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 16")
sample16mean<-mean(x.avg)
sample16sd<-sd(x.avg)
```

 The mean for this sample is `r sample16mean` and the standard deviation is `r sample16sd`.

```{r}
numb = 25
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 25")
sample25mean<-mean(x.avg)
sample25sd<-sd(x.avg)
```

The mean for this sample is `r sample25mean` and the standard deviation is `r sample25sd`.

```{r}
numb = 36
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 36")
sample36mean<-mean(x.avg)
sample36sd<-sd(x.avg)
```

The mean for this sample is `r sample36mean` and the standard deviation is `r sample36sd`.